\newsection
\section*{РЕФЕРАТ}

Объем работы равен \formbytotal{page}{страниц}{е}{ам}{ам}. Работа содержит \formbytotal{figurecnt}{иллюстраци}{ю}{и}{й}, \formbytotal{tablecnt}{таблиц}{у}{ы}{}, 50 библиографических источников и 12 листов графического материала. Количество приложений – 2. Графический материал представлен в приложении А. Фрагменты исходного кода представлены в приложении Б.

Перечень ключевых слов: сайт, система, html, php, css, медицинская лаборатория, пациенты, врачи, медсестры, валидация, база данных, форма, таблица, пользователь, пароль, защита информации, логин, главная страница, авторизация.

Целью выпускной квалификационной работы является помощь в организации процедур медицинской лаборатории, оперативность регистрации информации, удобство поиска информации и улучшение обслуживания пациентов.

Целью выпускной квалификационной работы является помощь\linebreak в организации процедур медицинской лаборатории, оперативность регистрации информации, удобство поиска информации и улучшение обслуживания пациентов.

При создании сайта использовался HTML и его CSS-плагины для создания визуально привлекательного дизайна и улучшения пользовательского опыта.

Целью выпускной квалификационной работы является помощь в организации процедур медицинской лаборатории, оперативность регистрации информации, удобство поиска информации и улучшение обслуживания пациентов.

В процессе создания сайта были созданы информационные блоки, использованы модули и функции, обеспечивающие работу с тематическими блоками, а также корректное функционирование сайта, разработаны разделы, содержащие специальности медицинской лаборатории, медицинские карты и карты пациентов.

Разработанный сайт будет внедрен в медицинской лаборатории.
\newpage
\selectlanguage{english}
\section*{ABSTRACT}
  
The volume of work is \formbytotal{page}{page}{}{s}{s}. The work contains \formbytotal{figurecnt}{illustration}{}{s}{s}, \formbytotal{tablecnt}{table}{}{s}{s}, 50 bibliographic sources and 12 sheets of graphic material. The number of applications is 2. The graphic material is presented in annex A. The layout of the site, including the connection of components, is presented in annex B.

List of keywords: website, system, html, php, css, clinical laboratory, patients, doctors, nurses, validation, database, form, table, user, password, data protection, login, main page, authorization.

The purpose of the graduate qualification work is to assist in the organization of medical laboratory procedures, expeditious registration of information, convenient information retrieval and improved patient care.

The purpose of the graduate qualification work is to help\linebreak in the organization of medical laboratory procedures, rapid registration of information, easy search for information and improve patient care.

HTML and its CSS plugins were used to create a visually appealing design and improve the user experience.

The purpose of the graduate qualification work is to help organize medical laboratory procedures, expeditious registration of information, easy search for information and improve patient care.

In the process of creating the site the information blocks were created, modules and functions were used to ensure the work with thematic blocks, as well as the correct functioning of the site, sections containing the specialties of the medical laboratory, medical records and patient records were developed.

The developed site will be implemented in the medical laboratory.
\selectlanguage{russian}
